---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
```

```{r setup}
library(cheetahR)
```

## Your first table

```{r}
# Render table
cheetah(iris)
```

## Customize columns

```{r}
# Change some feature of some columns in the data
cheetah(
  iris,
  columns = list(
    Sepal.Length = column_def(name = "Sepal_Length", width = 120),
    Sepal.Width = column_def(name = "Sepal_Width", width = 120),
    Petal.Length = column_def(name = "Petal_Length", width = 120),
    Petal.Width = column_def(name = "Petal_Width", width = 120),
    Species = column_def(name = "Species")
  )
)
```

## Customize `rownames`

The default for the row names column is `TRUE` if present in the data; however, to modify it, include a column definition with "rownames" as the designated column name.

```{r}
# Example of customizing rownames with color and width
cheetah(
  mtcars,
  columns = list(
    rownames = column_def(width = 150, style = list(color = "red"))
  )
)
```

## Defining the column types

The `column_type` parameter in `column_def()` allows you to specify different types of columns. There are 6 possible options:

- `"text"`: For text columns
- `"number"`: For numeric columns
- `"check"`: For checkbox columns
- `"image"`: For image columns
- `"radio"`: For radio button columns
- `"multilinetext"`: For multiline text columns

The `column_type` parameter is optional. If it is not specified, the column type will be inferred from the data type.

```{r}
# Using checkbox column type to indicate NA values
head(airquality, 10) %>%
  mutate(
    has_na = if_any(everything(), is.na),
    has_na = ifelse(has_na, "true", "false"),
    .before = 1
  ) %>%
  cheetah(
    columns = list(
      has_na = column_def(
        name = "Contains NA",
        column_type = "check",
        style = list(
          uncheckBgColor = "#FDD",
          checkBgColor = "rgb(255, 73, 72)",
          borderColor = "red"
        )
      )
    )
  )
```

## Cell messages

You can define __cell messages__ by passing a JS function wrapped within `htmlwidget::JS()`. This function takes a single
parameter `rec` which refers to data row. It must return an object with 2 properties:

- `type`: the message type. Valid types are `"info"`, `"warning"` and `"error"`.
- `message`: the message content. As shown below, you can use a [__ternary operator__](https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Operators/Conditional_operator) to check whether a condition is respected, for instance `rec.Species === 'setosa'` check if the recorded specie is `"setosa"`. Since `rec` refers to an entire data row, you can also target multiple columns in your check logic.

```{r}
cheetah(
  iris,
  columns = list(
    Species = column_def(
      action = "input",
      message = htmlwidgets::JS(
        "function(rec) {
          return {
            type: 'error',
            message: rec.Species === 'setosa' ? 'Invalid specie type.' : null,
          }
        }"
      )
    )
  )
)
```
